HO unification from object language to meta language

### 2024-02-06 main.tex
crazy

>>>>

\section{intro}

we are interested in using a meta language in LF style to write
automation, proof search. In various works... they achieve that
for a OL which is simpler than the LF, the equational theory is included
in the one of the ML. This is exploited to piggy back on the unif
of the ML.
the peculiarity of our setting is that the OL has a richer equational
theory of the ML, eg beta eta zeta bla bla. Moreover is HO logic, so
quantifies over functions, so unif variable range on that too.
We want to piggy back on the ML unif whenever the problem fits
in its domain, eg pattern fragment.
this is important for practical purposes.

\subsection{in a nutshell}
example, a rule for theorem
$$
forall f : A -> B, .. bla f .. -> prove (\forall x, f x)
bla g
$$
\begin{minted}{elpi}
type app ..
prove (forall x\ app F x) :- ... bla F ...
\end{minted}
on goal \mint{elpi}|prove (forall x\ app (app g x) x))|
would fail since \mint{elpi}|F != app g x|.

of course one wants to avoid
\begin{minted}{elpi}
prove P S S'' :- ol-unif P S (forall x\ app "F" x) S', ... assignment "F" S' F, bla F S' ...
\end{minted}

Now, ML has HO variables
\begin{minted}{elpi}
type lam ..
prove (forall x\ F x) :- ... bla F ...
\end{minted}
this time  \mint{elpi}|F x != app (app g x) x| has solution
\mint{elpi}|F = a\ app (app g x) x| but F is not a term so
bla needs to be adapted,
\begin{minted}{elpi}
prove (forall x\ F x) :- ... bla (lam F) ...
bla g.
\end{minted}
this is too simplistic since \mint{elpi}|g != lam x\ app g x|

\subsection{contribution}
\begin{itemize}
\item prover for HO OL in ML that uses unif
\item eta beta
\item test on stdpp and TLC
\end{itemize}
